Towards a Machine Learning approach for Aggregate Computing

### 2021-11-05 paper-2021-woa-ac-ml.tex
add hysteretic equation

For our first tests, 
 we decide to set up an Independent learning technique, by which each agent try to improve our current local policy.
 Our approach is partially inspired by Swarm Q-Learning~\cite{nguyen2018swarm} and leverage Hysteretic Q-Learning~\cite{hysteretic-q} to 
 handle
 the non-stationarity in the environment.
%
In particular, each agent maintains a local Q table ($Q_i(s, a)$, where i is the agent id) following the standard Hysteretic update:
$$
Q(s, a) = 
$$
At the end of the episodes, each agent has collected its local experience, which can vary in different zones. So, we combine the N q table
 selecting the maximum value for each state-action pair:
$$
Q_{max}(s, a) = max_i(Q_i(s, a))
$$
Then, in the new episode, each agent starts with the $Q_max$ and try to refine it. 
 This max combination works because we assume a homogeneous behaviour, where each agent perform
 in the same way when reaching the same state.

>>>>

For our first tests, 
 we decide to set up an Independent learning technique, by which each agent try to improve our current local policy.
 Our approach is partially inspired by Swarm Q-Learning~\cite{nguyen2018swarm} and leverage Hysteretic Q-Learning~\cite{hysteretic-q} to 
 handle
 the non-stationarity in the environment.
%
In particular, each agent maintains a local Q table ($Q_i(s, a)$, where i is the agent id) following the standard Hysteretic update:
$$
\delta \leftarrow r + \gamma * max_a Q_i(s', a) - Q_i(s_t, a_t)
$$
$$
Q(s_t, a_t) =  \begin{cases} 
  Q(s_t, a_t) + \alpha * \delta & \mbox{if } delta >= 0 \\ 
  Q(s_t, a_t) + \beta * \delta & \mbox{otherwise }
\end{cases}
$$

At the end of the episodes, each agent has collected its local experience, which can vary in different zones. So, we combine the N q table
 selecting the maximum value for each state-action pair:
$$
Q_{max}(s, a) = max_i(Q_i(s, a))
$$
Then, in the new episode, each agent starts with the $Q_max$ and try to refine it. 
 This max combination works because we assume a homogeneous behaviour, where each agent perform
 in the same way when reaching the same state.
